\section{Experience}

\HeadingsStart

% ----------------------------------------------------------------------

\HeadingTwoLines
{Data Scientist}{Dec. 2023 -- Present}
{HUK-Coburg}{Coburg, Germany}

% TODO: Add bullet points

% ----------------------------------------------------------------------

\HeadingTwoLines
{Data Science Intern}{Nov. 2022 -- Jan. 2023}
{eoda GmbH}{Kassel, Germany}

\ItemsStart
\Item{Implemented a Gradient Boosting classifier, enhancing yield potential prediction accuracy by 30\%.}
\Item{Developed an ML model forecasting electricity consumption of industrial machines.}
\Item{Boosted test coverage of two Python projects by up to 300\%.}
\Item{Updated Docker images and CI/CD pipelines.}
\ItemsEnd

% ----------------------------------------------------------------------

\HeadingTwoLines
{Teaching Assistant}{Oct. 2021 -- Sep. 2022}
{University of Göttingen, Econometrics}{Göttingen, Germany}

\ItemsStart
\Item{Led weekly tutorials for the master's course \emph{Econometrics I}.}
\Item{Responsible for student queries and exam grading; tripled tutorial attendance.}
\ItemsEnd

% ----------------------------------------------------------------------

\HeadingTwoLines
{Research Assistant}{April 2021 -- April 2022}
{University of Göttingen, Chair of Statistics}{Göttingen, Germany}

\ItemsStart
\Item{Contributed to the \href{https://github.com/liesel-devs/liesel}{Liesel project}, an R \& Python Bayesian regression framework.}
\Item{Enhanced MCMC sampling with visual diagnostics and convergence checks.}
\Item{Authored two detailed tutorials for the \href{https://liesel.readthedocs.io/en/latest/}{Liesel documentation}.}
\ItemsEnd

% ----------------------------------------------------------------------

\HeadingTwoLines
{Content Creation Intern}{March 2020 -- June 2020}
{Studybees GmbH}{Mannheim, Germany}

\ItemsStart
\Item{Crafted two video courses for \href{https://studybees.de/}{Studybees}, focusing on advanced statistics and econometrics.}
\Item{Produced 50+ instructional videos, totaling 10+ hours.}
\ItemsEnd

% ----------------------------------------------------------------------

\HeadingTwoLines
{Teaching Assistant}{Sep. 2018 -- March 2020}
{University of Mannheim, Stochastics}{Mannheim, Germany}

\ItemsStart
\Item{Conducted weekly tutorials for the bachelor's course \emph{Stochastics I} at the Faculty of Mathematics.}
\Item{Assessed weekly assignments and exams, covering probability and measure theory.}
\ItemsEnd

% ----------------------------------------------------------------------

\HeadingTwoLines
{Social Service Volunteer}{Aug. 2015 -- Aug. 2016}
{TBS Saarbrücken}{Saarbrücken, Germany}

\ItemsStart
\Item{Coached children (1-16 years) in six sports; acquired track and field athletics license.}
\Item{Organized a summer festival for 200+ attendees.}
\ItemsEnd

\HeadingsEnd
